Unbiased pangenome graphs

### 2022-10-08 manuscript/main.tex
fix incomplete sentence

It is also a potentially novel approach.
Despite the existence of many methods for pangenome building, we are not aware of any comparable method which can losslessly convert an all-to-all alignment to a variation graph.
This direct relationship allows users to adjust the shape of the resulting graph by modifying alignment parameters, allowing the design of custom graph construction processes based on domain-specific knowledge and potentially manual curation of assembly alignments.
In contrast to existing methods, which depend on particular structuring of their input \citep{Li:2020,Armstrong:2020}, \textit{seqwish} is unbiased in that as it directly and uniformly represents sequence relationships given on input in the resulting graph.
Our comparison with related pangenome graph-building methods demonstrates that these effects can be significant.
\textit{minigraph}'s output varies substantially, with $\sigma \approx 1.25\%$ of graph length for a 7-chromosome input with approximately $99.3\%$ pairwise identity.
De Bruijn graph methods, which are also unbiased with their treatment of input genomes \citep{Minkin_2016,Sheikhizadeh_2016,Yu_2021}.
%However, our approach is different than these, and allows the direct

>>>>

It is also a potentially novel approach.
Despite the existence of many methods for pangenome building, we are not aware of any comparable method which can losslessly convert an all-to-all alignment to a variation graph.
This direct relationship allows users to adjust the shape of the resulting graph by modifying alignment parameters, allowing the design of custom graph construction processes based on domain-specific knowledge and potentially manual curation of assembly alignments.
In contrast to existing methods, which depend on particular structuring of their input \citep{Li:2020,Armstrong:2020}, \textit{seqwish} is unbiased in that as it directly and uniformly represents sequence relationships given on input in the resulting graph.
Our comparison with related pangenome graph-building methods demonstrates that these effects can be significant.
\textit{minigraph}'s output varies substantially, with $\sigma \approx 1.25\%$ of graph length for a 7-chromosome input with approximately $99.3\%$ pairwise identity.
Although we did not compare with de Bruijn graph methods, which are also unbiased with their treatment of input genomes \citep{Minkin_2016,Sheikhizadeh_2016,Yu_2021}, we believe such methods are fundamentally different in that because they collapse all exact matches of a given length k.
This prevents high-level structuring of patterns of homology and orthology in the resulting graph, and they furthermore cannot be guided by a specific alignment set.
%However, our approach is different than these, and allows the direct
